\section{\textbf{Abstract}} \label{sec abstract} 

\par Magic state distillation is a key technique in fault-tolerant quantum computing that allows the implementation of non-Clifford gates -- namely the T gate -- using only operations that are, themselves, fault-tolerant under stabilizer codes. Stabilizer codes can perform Clifford gates: \textsc{Hadamard}, \textsc{CNOT}, and \textsc{P}, reliably and efficiently. However, Clifford gates alone are not universal for quantum computation. A non-Clifford gate is required to achieve full computational power and finding stabilizer codes that implement such gates fault tolerantly are rare. Moreover, both codes must have good distance (number of detectable errors) for the resources/qubits used.
\\  \\
\par The \textbf{Easten-Knill Theorem} states that no singular quantum error correcting code can implement both the Clifford group of gates and a Non-Clifford gate transversally (i.e fault tolerantly) simultaneously. Magic state distillation solves this problem by preparing many noisy copies of a special quantum state called a \textit{\textbf{magic state}}. This allows one to use Clifford operations and measurements to purify these states, detecting and discarding those affected by noise. \\ \\
\par Through iterative rounds of this purification, a small number of high-fidelity magic states are obtained, which can then be used in the computation to simulate fault-tolerant \textsc{T} gates. Although resource-intensive - requiring large overhead in qubits and operations - magic state distillation is currently the most practical method to achieve universal, error-corrected quantum computation. However, not all codes have equal yields for creating these \textit{\textbf{magic state}}, and the utility of many qubit and prime qudit codes is derived from the fidelity and efficacy with which they can be used to distill magic states.
\\ \\
\par In our project, we explored magic state distillation yields for families of doubled quadratic residue (QR) based \textsc{CSS} codes as constructed by Jain and Albert. There are three overlapping families described: doubly even QR \textsc{CSS} codes, weak triply even codes obtained via doubling QR codes and, triorthogonal codes obtained by doubling self dual codes. The latter two codes are promising candidates for a Bravyi-Haah style triorthogonal block distillation protocol, as the weak triply even codes requires no clifford corrections and both provide high order error suppression at high distances.
For multiple qubit diagonal circuits (many \textsc{CCZ} gates, adders, etc.) the same codes can also be used in Campbell-Howard synthillation.


